Deep mutational scanning of hemagglutinin helps identify evolutionarily successful human H3N2 influenza viruses

### 2018-02-01 paper/manuscript.tex
Add Katie edit
Add mut effect plot to supp post-Perth2009 figure

\subsection*{Creation of MDCK-SIAT1-TMPRSS2 cells}
When growing influenza virus in cell culture, trypsin is normally added in order to cleave HA into its mature form.
To obviate the need for trypsin, we engineered an MDCK-SIAT1 cell line to constitutively express the TMPRSS2 protease, which cleaves and activates HA in the human airways~\cite{bottcher2006proteolytic,bottcher2010cleavage}.
The human TMPRSS2 cDNA ORF was ordered from OriGene (NM\_005656) and cloned into a pHAGE2 lentiviral vector under an EF1$\alpha$-Int promoter followed by an IRES driving expression of mCherry to create plasmid pHAGE2-EF1aInt-TMPRSS2-IRES-mCherry-W.
We used the lentiviral vector to transduce MDCK-SIAT1 cells, and sorted an intermediate mCherry population by flow cytometry.
We refer to the sorted bulk population as MDCK-SIAT1-TMPRSS2 cells.
There is no selectable marker for the TMPRSS2; however, we maintain the cells at low passage number, and have seen no indication that they lose their ability to support the growth of viruses with H3 HAs in the absence of exogenous trypsin.

@@

\begin{suppfigure}
\centerline{\includegraphics[width=0.75\textwidth]{figs/S04_post_Perth2009/post_Perth2009_seqpref.pdf}}
\caption{\label{suppfig:future}
{\bf The sequence preference of nodes that occur after the split of Perth/2009 off the trunk.}
Our experiments show a selective advantage for the trunk even if we limit the analysis to sequences that occur after the split of Perth/2009 off the trunk.
(A) Phylogenetic tree showing all nodes that branch from the trunk before or contemporaneously with Perth/2009 (orange), all nodes that occur after the branch to Perth/2009 for which we can resolve the trunk (red) or side branches (blue), and all nodes for which it is not yet clear which sequences will be on the trunk or side branches (gray).
In this figure, we restrict the analysis to the nodes in red and blue.
(B)  
Average per-site sequence preference (similar to Figure~\ref{fig:trunkvssidebranch}C) for all trunk and side-branch nodes that occur after the branch to Perth/2009.
(C)
The sequence preferences of nodes on the trunk generally exceed those of nodes on the side branches along the post-Perth/2009 portion of the tree.
Note that because there are relatively few post-Perth/2009 sequences for which we can currently distinguish trunk from side branch, the number of points in this plot is small, precluding meaningful statistical analyses of the type performed in Figure~\ref{fig:trunkvssidebranch}B.
}
\end{suppfigure}

\begin{suppfigure}
\centerline{\includegraphics[width=0.6\textwidth]{figs/S05_seqpref_zoomed/seqpref_zoomed.pdf}}
\caption{\label{suppfig:seqpref_zoomed}
{\bf The per-site sequence preference at epitope and non-epitope sites.}
The per-site sequence preferences shown in Figure~\ref{fig:sequence_preference}B, but on separate y-axes.
}
\end{suppfigure}

>>>>

\subsection*{Creation of MDCK-SIAT1-TMPRSS2 cells}
When growing influenza virus in cell culture, trypsin is normally added in order to cleave HA into its mature form.
To obviate the need for trypsin, we engineered an MDCK-SIAT1 cell line to constitutively express the TMPRSS2 protease, which cleaves and activates HA in the human airways~\cite{bottcher2006proteolytic,bottcher2010cleavage}.
The human TMPRSS2 cDNA ORF was ordered from OriGene (NM\_005656) and cloned into a pHAGE2 lentiviral vector under an EF1$\alpha$-Int promoter followed by an IRES driving expression of mCherry to create plasmid pHAGE2-EF1aInt-TMPRSS2-IRES-mCherry-W.
We used the lentiviral vector to transduce MDCK-SIAT1 cells, and sorted an intermediate mCherry-positive population by flow cytometry.
We refer to the sorted bulk population as MDCK-SIAT1-TMPRSS2 cells.
There is no selectable marker for the TMPRSS2; however, we maintain the cells at low passage number, and have seen no indication that they lose their ability to support the growth of viruses with H3 HAs in the absence of exogenous trypsin.

@@

\begin{suppfigure}
\centerline{\includegraphics[width=0.75\textwidth]{figs/S04_post_Perth2009/post_Perth2009_seqpref.pdf}}
\caption{\label{suppfig:future}
{\bf The sequence preference of nodes that occur after the split of Perth/2009 off the trunk.}
Our experiments show a selective advantage for the trunk even if we limit the analysis to sequences that occur after the split of Perth/2009 off the trunk.
(A) Phylogenetic tree showing all nodes that branch from the trunk before or contemporaneously with Perth/2009 (orange), all nodes that occur after the branch to Perth/2009 for which we can resolve the trunk (red) or side branches (blue), and all nodes for which it is not yet clear which sequences will be on the trunk or side branches (gray).
In this figure, we restrict the analysis to the nodes in red and blue.
(B)  
Average per-site sequence preference (similar to Figure~\ref{fig:trunkvssidebranch}C) for all trunk and side-branch nodes that occur after the branch to Perth/2009.
(C)
The sequence preferences of nodes on the trunk generally exceed those of nodes on the side branches along the post-Perth/2009 portion of the tree.
(D)
Post-Perth/2009 trunk mutations on average tend to be more favorable than side branch mutations.
Note that there are relatively few post-Perth/2009 mutations (13 trunk mutations and 324 side branch mutations).
}
\end{suppfigure}
